Fuzzy Extractors for Noisy Sources with More Errors Than Entropy

### 2015-02-10 trunk/constantRate/ConstCompFuzzExt-crypto.tex
minor edits and notation change from dissertation

\newcommand{\class}[1]{{\ensuremath{\mathsf{#1}}}}
\newcommand{\gen}{\ensuremath{\class{Gen}}\xspace}
\newcommand{\rep}{\ensuremath{\class{Rep}}\xspace}
\newcommand{\sketch}{\ensuremath{\class{SS}}\xspace}
\newcommand{\rec}{\ensuremath{\class{Rec}}\xspace}
\newcommand{\enc}{\ensuremath{\class{Enc}}\xspace}
\newcommand{\dec}{\ensuremath{\class{Dec}}\xspace}
\newcommand{\prg}{\ensuremath{\class{prg}}\xspace}
\newcommand{\zo}{\ensuremath{\{0, 1\}}}
\newcommand{\vect}[1]{\ensuremath{\mathbf{#1}}}
\newcommand{\zq}{\ensuremath{\mathbb{Z}_q}}
\newcommand{\Fq}{\ensuremath{\mathbb{F}_q}}
\newcommand{\sample}{\ensuremath{\class{Sample}}\xspace}
\newcommand{\neigh}{\ensuremath{\class{Neigh}}\xspace}
\newcommand{\dis}{\ensuremath{\mathsf{dis}}}
\newcommand{\decode}{\ensuremath{\mathsf{Decode}}}
\newcommand{\guess}{\mathsf{guess}}

@@

Our third construction provides information-theoretic, rather than computational, security. It works for \emph{sparse block sources}. These are sources in which a sufficient fraction of the symbols have entropy conditioned on previous blocks. It uses symbols-by-symbol condensers to reduce the alphabet size while preserving most of the entropy, and then applies existing fuzzy extractors to the resulting string.

@@

\begin{table}
\begin{center}
\begin{tabular}{l l l l l}
  & Source Structure & Error Rate  & Techniques\\
\hline
Cons. \ref{cons:sampling} (reusable)  & high-entropy samples & any subconstant &  Sample-then-obfuscate \\
Cons. \ref{cons:first construction}  & sparse high-entropy  marginals & constant &  Error-correct-and-obfuscate\\
Cons. \ref{cons:info theoretic} (info-theoretic)   & sparse block source  & constant & Condense-then-fuzzy-extract\\
\hline\end{tabular}
\end{center}
%end centering
\caption{Summary of new constructions.  }
\label{tab:upper bounds}
\end{table}

@@

%In this work we restrict the distribution of the original reading $w$ and allow $w'$ to be an arbitrary point within distance $t$.  An alternative approach is to restrict the set of $w'$ where $\gen$ produces the correct key. \lnote{move this somewhere that makes more sense, probably above where we talk about a ball around a $w'$ and the obvious impossibility}%  A meaningful restriction of correctable errors is an open problem. 
%\fi

\medskip
\paragraph{Organization }
The remainder of this paper is organized as follows: we cover notation and fuzzy extractors in \secref{sec:preliminaries}.  We present our information-theoretic construction in \secref{sec:info theory cons} and our two computational constructions in Sections \ref{sec:sampling} and \ref{sec:cor construction}.

@@

\begin{definition}~\cite[Definition 2.5]{fuller2013computational}
\label{def:comp fuzzy extractor}
Let $\mathcal{W}$ be a family of probability distributions over $\mathcal{M}$. A pair of randomized procedures ``generate'' ($\gen$) and ``reproduce'' ($\rep$) is an $(\mathcal{M}, \mathcal{W}, \kappa, t)$-\emph{computational fuzzy extractor} that is $(\epsilon_{sec}, s_{sec})$-hard with error $\delta$ if \gen and \rep satisfy the following properties:
\begin{itemize}
\item The generate procedure \gen on input $w\in \mathcal{M}$ outputs an extracted string $r\in\{0,1\}^\kappa$ and a helper string $p\in\{0,1\}^*$.
\item The reproduction procedure \rep takes an element $w'\in\mathcal{M}$ and a bit string $p\in\{0,1\}^*$ as inputs.  The \emph{correctness} property guarantees that if $\dis(w, w')\leq t$ and $(r, p)\leftarrow \gen(w)$, then $\Pr[\rep( w', p) = r] \geq 1-\delta$, where the probability is over the randomness of $(\gen, \rep)$.
If $\dis(w, w') > t$, then no guarantee is provided about the output of \rep.
\item The \emph{security} property guarantees that for any distribution $W\in \mathcal{W}$, the string $r$ is pseudorandom conditioned on $p$, that is $\delta^{\mathcal{D}_{s_{sec}}}((R, P), (U_\kappa, P))\leq \epsilon_{sec}$.
\end{itemize}
\end{definition}
In the above definition, the errors are chosen before $P$: if the error pattern between $w$ and $w'$ depends on the output of $\gen$, then there is no guarantee about the probability of correctness. In Constructions~\ref{cons:sampling} and~\ref{cons:first construction} it is crucial that $w'$ is chosen independently of the outcome of \gen.

@@

\paragraph{Sources with High-Entropy Samples}
Let the source $W=W_1, \dots, W_\gamma$ consist of strings of length $\gamma$ over some arbitrary alphabet $\mathcal{Z}$. For some parameters $\eta, \subsetEntropy$, we say that the source $W$ is a source with  \emph{$(\eta, \subsetEntropy)$-high-entropy samples} if $\Hav(w_{j_1}, \dots, w_{j_\eta}\, |\, j_1, \dots, j_\eta)>\subsetEntropy$ for uniformly random distinct $1< j_1, \dots, j_\eta \le \gamma$. This property can hold, for example, if the symbols $W_i$ are $\eta$-wise independent, and each has entropy at least $\subsetEntropy/\eta$. However, that's not the only way for the property to hold: for example, we can allow sources in which some symbols have little entropy or depend on other symbols, by simply choosing a larger $\eta$ to compensate.

@@

\subsection{Reusability of \consref{cons:sampling}}
\lnote{haven't looked at this---may need work}
The reusability of \consref{cons:sampling} follows from the security of the VGB obfuscator with auxiliary input.  We consider a bounded $q = \poly(n)$ number of reuses.  For some fixed $i\in \{1,..., q\}$ we will treat the remaining keys as auxiliary input to the adversary, and the simulator still performs comparably to a distinguisher with access to the obfuscations.  Thus, given sufficiently strong reusability we achieve the following result:

\begin{theorem}
\label{thm:reusability}
Let $q = \poly(n)$, and let all the variables be as in \thref{thm:sampling}, except that $\mathcal{O}$ be an $\ell\times q$-composable VGB obfuscator for digital lockers~(with $\kappa$ bit outputs) with auxiliary inputs.  For any admissible $f_2,..., f_q$, for all $s_{sec} = \poly(n)$ there exists some $\epsilon_{sec} = \ngl(n)$ such that $(\gen, \rep)$ is $(q, \epsilon_{sec}, s_{sec}, f_2,..., f_q)$-reusable fuzzy extractor.
\end{theorem}
\begin{proof}
The only modification to the outline presented in \secref{ssec:sec cons sampling} is in \lemref{lem:samp unguess} with the other keys $R_1,..., R_{i-1}, R_{i+1}, ..., R_q$ treated as additional auxiliary input to the adversary/simulator.  The simulator in the definition of composable obfuscation is required to function for arbitrary circuits in the family even if the choice of these circuits depends on the previous obfuscations.  Thus allows reading $w_i$ to be chosen depending on public values $p_1,..., p_{i-1}$.
\bnote{say more here?}
\end{proof}

@@

Before presenting the construction we provide some definitions from error correcting codes.
We use error-correct codes over $\{0,1\}^\gamma$ which correct up to $t$ bit flips from $0$ to $1$ but no bit flips from $1$ to $0$ (this is the Hamming analog of the $Z$-channel~\cite{tallini2002capacity}).\footnote{Any code that corrects $t$ Hamming errors also corrects $t$ $0\rightarrow 1$ errors, but more efficient codes  exist for this type of error~\cite{tallini2002capacity}.
Codes with $2^{\Theta(\gamma)}$ codewords and $t = \Theta(\gamma)$ over the binary alphabet exist for Hamming errors and suffice for our purposes~(first constructed by Justensen~\cite{justesen1972class}).  These codes also yield a constant error tolerance for $0\rightarrow 1$ bit flips.
The class of errors we support in our source~($t$ Hamming errors over a large alphabet) and the class of errors for which we need codes~($t$ $0\rightarrow 1$ errors) are different.
}
\begin{definition}
\label{def:hamming z channel}
For a point $c\in \zo^\gamma$ define $\neigh_t(c) $ as the set of all points where at most $t$ bits $c_i$ are changed from $0$ to $1$.
\end{definition}

\begin{definition}
Let $\neigh_t(c)$ be as in \defref{def:hamming z channel}.  Then a set $C$~(over $\zo^\gamma$) is a $(\neigh_t, \delta_{code})$-code if there exists an efficient procedure $\decode$ such that $\Pr_{c\in C}[\exists c'\in \neigh_t(c) \text{ s.t. } \decode(c') \neq c] \leq \delta_{code}$.
\end{definition}
\bnote{these are quite strange.  changing them for dissertation.  update if accepted.}

\begin{construction}
\label{cons:first construction}
Let $\mathcal{Z}$ be an alphabet and let $W = W_1,..., W_\gamma$ be a distribution over $\mathcal{Z}^\gamma$.  Let $\mathcal{O}$ be an obfuscator for point functions with points from $\mathcal{Z}$.  Let  $C\subset \zo^\gamma$ be an error-correcting code.
We describe $\gen, \rep$ as follows:

@@

Unfortunately, \consref{cons:first construction} is not a computational fuzzy extractor.  The codewords $c$ are not uniformly distributed and it is possible to learn some bits of $c$~(for the symbols of $W$ without much entropy).  However, we can show that $c$ looks like it has entropy.  We use the notion of HILL entropy~\cite{DBLP:journals/siamcomp/HastadILL99} extended to the conditional case:
\begin{definition}\protect{~\cite[Definition 3]{DBLP:conf/eurocrypt/HsiaoLR07}}
\label{def:hill ent}
Let $(W, S)$ be a pair of random variables.  $W$ has
\emph{HILL entropy} at least $k$ conditioned on $S$,
denoted $H^{\hill}_{\epsilon_{sec}, s_{sec}}(W|S)\geq k$ if there exists a joint distribution $(X, S)$, such that $\Hav(X|S)\geq k$ and $\delta^{\mathcal{D}_{s_{sec}}} ((W, S),(X,S))\leq \epsilon_{sec}$.
\end{definition}
We now define a weaker object that outputs computational entropy~(instead of a pseudorandom key).  We call this object a computational fuzzy conductor.  It is the computational analogue of a fuzzy conductor~(introduced by Kanukurthi and Reyzin~\cite{KanukurthiR09}).
\begin{definition}
\label{def:comp fuzzy cond}
A pair of randomized procedures ``generate'' ($\gen$) and ``reproduce'' ($\rep$) is an $(\mathcal{M}, \mathcal{W}, \tilde{m}, t$)-computational fuzzy conductor that is $(\epsilon_{sec}, s_{sec})$-hard with error $\delta$ if $\gen$ and $\rep$ satisfy \defref{def:comp fuzzy extractor}, except the last condition is replaced with the following weaker condition:
\begin{itemize}
\item for any distribution $W\in \mathcal{W}$, the string $r$ has high HILL entropy conditioned on $P$.  That is $H^{\hill}_{\epsilon_{sec}, s_{sec}}(R |P)\geq \tilde{m}$.
\end{itemize}
\end{definition}
Computational fuzzy conductors can be converted to computational fuzzy extractors using standard techniques~(see \apref{sec:further defs}).
The following theorem states the construction is a computational fuzzy conductor~(proof in \apref{sec:construction analysis}).
\begin{theorem}
\label{thm:main thm first cons}
Let $n$ be a security parameter. Let $\mathcal{Z}$ be an alphabet where $|\mathcal{Z}| \ge 2^{ \omega(\log(n))}$.
Let $\mathcal{W}$ be a family of $(q,\alpha= \omega(\log n),  \beta)$-unguessable block sources over $\mathcal{Z}^\gamma$, for any $q = \poly(n)$.  Furthermore, let $C$ be a $(\neigh_t, \delta_{code})$-code over $\mathcal{Z}^\gamma$.  Let $\mathcal{O}$ be an $\gamma$-composable VGB obfuscator for point functions with auxiliary inputs. Then for any $s_{sec} = \poly(n)$ there exists some $\epsilon_{sec}=\ngl(n)$ such that \consref{cons:first construction} is a $(\mathcal{Z}^\gamma, \mathcal{W}, \tilde{m}=H_0(C)-\beta, t)$-computational fuzzy conductor that is $(\epsilon_{sec}, s_{sec})$-hard with error $\delta_{code} + \gamma/|\mathcal{Z}|$.
\end{theorem}

@@

We adapt the definition of Boyen to the computational setting~(\defref{def:outsider fuzz ext}).  
The definition of Boyen considers a single adversary.  We split the adversary into two parts, one of which is information-theoretic and another that is computationally bounded.  The functions $f_2,..., f_q$ can be thought of as a single adversary that sees all prior state.  However, to provide meaningful security in the computational setting, we cannot have communication between these adversaries.\footnote{An alternative would be to have a single computationally bounded adversary.  \consref{cons:sampling} satisfies this alternative adaption as well.}
Because these two adversaries do not communicate we strengthen the definition by allowing the perturbation functions,  $f_i$, to see the original sample $w_1$.  This was not allowed in the definition of Boyen as it would make security impossible.

>>>>

\newcommand{\class}[1]{{\ensuremath{\mathsf{#1}}}}
\newcommand{\gen}{\ensuremath{\class{Gen}}\xspace}
\newcommand{\rep}{\ensuremath{\class{Rep}}\xspace}
\newcommand{\sketch}{\ensuremath{\class{SS}}\xspace}
\newcommand{\rec}{\ensuremath{\class{Rec}}\xspace}
\newcommand{\enc}{\ensuremath{\class{Enc}}\xspace}
\newcommand{\dec}{\ensuremath{\class{Dec}}\xspace}
\newcommand{\prg}{\ensuremath{\class{prg}}\xspace}
\newcommand{\zo}{\ensuremath{\{0, 1\}}}
\newcommand{\vect}[1]{\ensuremath{\mathbf{#1}}}
\newcommand{\zq}{\ensuremath{\mathbb{Z}_q}}
\newcommand{\Fq}{\ensuremath{\mathbb{F}_q}}
\newcommand{\sample}{\ensuremath{\class{Sample}}\xspace}
\newcommand{\neigh}{\ensuremath{\class{Neigh}}\xspace}
\newcommand{\error}{\ensuremath{\class{Err}}\xspace}
\newcommand{\weight}{\ensuremath{\class{Wgt}}\xspace}
\newcommand{\dis}{\ensuremath{\mathsf{dis}}}
\newcommand{\decode}{\ensuremath{\mathsf{Decode}}}
\newcommand{\guess}{\mathsf{guess}}

@@

Our third construction provides information-theoretic, rather than computational, security. It works for \emph{sparse block sources}. These are sources in which a sufficient fraction of the symbols have entropy conditioned on previous blocks. It uses symbol-by-symbol condensers to reduce the alphabet size while preserving most of the entropy, and then applies existing fuzzy extractors to the resulting string.

@@

\begin{table}
\begin{center}
\begin{tabular}{l l l l l}
  & Source Structure & Error Rate  & Techniques\\
\hline
Cons. \ref{cons:sampling} (reusable)  & high-entropy samples & any subconstant &  Sample-then-obfuscate \\
Cons. \ref{cons:first construction}  & sparse high-entropy  marginals & constant &  Error-correct-and-obfuscate\\
Cons. \ref{cons:info theoretic} (info-theoretic)   & sparse block source  & constant & Condense-then-fuzzy-extract\\
\hline\end{tabular}
\end{center}
%end centering
\caption{Summary of new constructions. \consref{cons:sampling} supports the widest class of sources.  The sources supported by the other sources are subsets of high-entropy samples.  \consref{cons:first construction} and \consref{cons:info theoretic} support incomparable classes of sources.}
\label{tab:upper bounds}
\end{table}

@@

%In this work we restrict the distribution of the original reading $w$ and allow $w'$ to be an arbitrary point within distance $t$.  An alternative approach is to restrict the set of $w'$ where $\gen$ produces the correct key. \lnote{move this somewhere that makes more sense, probably above where we talk about a ball around a $w'$ and the obvious impossibility}%  A meaningful restriction of correctable errors is an open problem. 
%\fi
\paragraph{Organization }
The remainder of this paper is organized as follows: we cover notation and fuzzy extractors in \secref{sec:preliminaries}.  We present our information-theoretic construction in \secref{sec:info theory cons} and our two computational constructions in Sections \ref{sec:sampling} and \ref{sec:cor construction}.

@@

\begin{definition}~\cite[Definition 2.5]{fuller2013computational}
\label{def:comp fuzzy extractor}
Let $\mathcal{W}$ be a family of probability distributions over $\mathcal{M}$. A pair of randomized procedures ``generate'' ($\gen$) and ``reproduce'' ($\rep$) is an $(\mathcal{M}, \mathcal{W}, \kappa, t)$-\emph{computational fuzzy extractor} that is $(\epsilon_{sec}, s_{sec})$-hard with error $\delta$ if \gen and \rep satisfy the following properties:
\begin{itemize}
\item The generate procedure \gen on input $w\in \mathcal{M}$ outputs an extracted string $r\in\{0,1\}^\kappa$ and a helper string $p\in\{0,1\}^*$.
\item The reproduction procedure \rep takes an element $w'\in\mathcal{M}$ and a bit string $p\in\{0,1\}^*$ as inputs.  The \emph{correctness} property guarantees that if $\dis(w, w')\leq t$ and $(r, p)\leftarrow \gen(w)$, then $\Pr[\rep( w', p) = r] \geq 1-\delta$, where the probability is over the randomness of $(\gen, \rep)$.
\item The \emph{security} property guarantees that for any distribution $W\in \mathcal{W}$, the string $r$ is pseudorandom conditioned on $p$, that is $\delta^{\mathcal{D}_{s_{sec}}}((R, P), (U_\kappa, P))\leq \epsilon_{sec}$.
\end{itemize}
\end{definition}
In the above definition, the errors are chosen before $P$: if the error pattern between $w$ and $w'$ depends on the output of $\gen$, then there is no guarantee about the probability of correctness. In Constructions~\ref{cons:sampling} and~\ref{cons:first construction} it is crucial that $w'$ is chosen independently of the outcome of \gen.

@@

\paragraph{Sources with High-Entropy Samples}
Let the source $W=W_1, \dots, W_\gamma$ consist of strings of length $\gamma$ over some arbitrary alphabet $\mathcal{Z}$. For some parameters $\eta, \subsetEntropy$, we say that the source $W$ is a source with  \emph{$(\eta, \subsetEntropy)$-high-entropy samples} if $\Hav(W_{j_1}, \dots, W_{j_\eta}\, |\, j_1, \dots, j_\eta)>\subsetEntropy$ for uniformly random distinct $1< j_1, \dots, j_\eta \le \gamma$. This property can hold, for example, if the symbols $W_i$ are $\eta$-wise independent, and each has entropy at least $\subsetEntropy/\eta$. However, that's not the only way for the property to hold: for example, we can allow sources in which some symbols have little entropy or depend on other symbols, by simply choosing a larger $\eta$ to compensate.

@@

\subsection{Reusability of \consref{cons:sampling}}
The reusability of \consref{cons:sampling} follows from the security of the VGB obfuscator with auxiliary input. Consider any $q = \poly(n)$ number of reuses.  For each fixed $i\in \{1,..., q\}$, we can treat the keys $r_1,\dots, r_{i-1}, r_{i+1}, \dots, r_q$ and the strings $p_1, \dots, p_q$ as auxiliary input to the obfuscation adversary. The result follows by simulatability of this adversary, using the same argument as the proof of Theorem~\label{thm:sampling} in \apref{sec:analysis sampling} (note that the simulator in the definition of composable obfuscation is required to function for arbitrary circuits in the family even if the choice of these circuits depends on the previous obfuscations, which allows reading $w_i$ to be chosen depending on public values $p_1,..., p_{i-1}$).

  Thus, given sufficiently strong reusability we achieve the following result:

\begin{theorem}
\label{thm:reusability}
Let $q = \poly(n)$, and let all the variables be as in \thref{thm:sampling}, except that $\mathcal{O}$ is an $\ell\times q$-composable VGB obfuscator for digital lockers~(with $\kappa$ bit outputs) with auxiliary inputs.  For any admissible $f_2,..., f_q$, for all $s_{sec} = \poly(n)$ there exists some $\epsilon_{sec} = \ngl(n)$ such that $(\gen, \rep)$ is $(q, \epsilon_{sec}, s_{sec}, f_2,..., f_q)$-reusable fuzzy extractor.
\end{theorem}

@@

Before presenting the construction we provide some definitions from error correcting codes.
We use error-correct codes over $\{0,1\}^\gamma$ which correct up to $t$ bit flips from $0$ to $1$ but no bit flips from $1$ to $0$ (this is the Hamming analog of the $Z$-channel~\cite{tallini2002capacity}).\footnote{Any code that corrects $t$ Hamming errors also corrects $t$ $0\rightarrow 1$ errors, but more efficient codes  exist for this type of error~\cite{tallini2002capacity}.
Codes with $2^{\Theta(\gamma)}$ codewords and $t = \Theta(\gamma)$ over the binary alphabet exist for Hamming errors and suffice for our purposes~(first constructed by Justensen~\cite{justesen1972class}).  These codes also yield a constant error tolerance for $0\rightarrow 1$ bit flips.
The class of errors we support in our source~($t$ Hamming errors over a large alphabet) and the class of errors for which we need codes~($t$ $0\rightarrow 1$ errors) are different.
}
\begin{definition}
\label{def:hamming z channel}
Let $e, c\in \zo^\gamma$ be vectors.  Let $x = \error(c, e)$ be defined as follows
\[x_i = \begin{cases} 1 & c_i=1 \vee e_i=1\\
0& \text{ otherwise}.\end{cases}\]
\end{definition}

\begin{definition}
A set $C$~(over $\zo^\gamma$) is a $(t, \delta_{code})$-Z code if there exists an efficient procedure $\decode$ such that \[\forall e \in \zo^\gamma | \weight(e)\le t, \Pr_{c\in C}[\decode(\error(c,e)) \neq c] \leq \delta_{code}.\]
\end{definition}

\begin{construction}
\label{cons:first construction}
Let $\mathcal{Z}$ be an alphabet and let $W = W_1,..., W_\gamma$ be a distribution over $\mathcal{Z}^\gamma$.  Let $\mathcal{O}$ be an obfuscator for point functions with points from $\mathcal{Z}$.  Let  $C\subset \zo^\gamma$ be $(t, \delta_{code})$-Z code.
We describe $\gen, \rep$ as follows:

@@

Unfortunately, \consref{cons:first construction} is not a computational fuzzy extractor.  The codewords $c$ are not uniformly distributed and it is possible to learn some bits of $c$~(for the symbols of $W$ without much entropy).  However, we can show that $c$ looks like it has entropy.  We use the notion of HILL entropy~\cite{DBLP:journals/siamcomp/HastadILL99} extended to the conditional case:
\begin{definition}\protect{~\cite[Definition 3]{DBLP:conf/eurocrypt/HsiaoLR07}}
\label{def:hill ent}
Let $(W, S)$ be a pair of random variables.  $W$ has
\emph{HILL entropy} at least $k$ conditioned on $S$,
denoted $H^{\hill}_{\epsilon_{sec}, s_{sec}}(W|S)\geq k$ if there exists a joint distribution $(X, S)$, such that $\Hav(X|S)\geq k$ and $\delta^{\mathcal{D}_{s_{sec}}} ((W, S),(X,S))\leq \epsilon_{sec}$.
\end{definition}
We now define a weaker object that outputs computational entropy~(instead of a pseudorandom key).  We call this object a computational fuzzy conductor.  It is the computational analogue of a fuzzy conductor~(introduced by Kanukurthi and Reyzin~\cite{KanukurthiR09}).
\begin{definition}
\label{def:comp fuzzy cond}
A pair of randomized procedures ``generate'' ($\gen$) and ``reproduce'' ($\rep$) is an $(\mathcal{M}, \mathcal{W}, \tilde{m}, t$)-computational fuzzy conductor that is $(\epsilon_{sec}, s_{sec})$-hard with error $\delta$ if $\gen$ and $\rep$ satisfy \defref{def:comp fuzzy extractor}, except the last condition is replaced with the following weaker condition:
\begin{itemize}
\item for any distribution $W\in \mathcal{W}$, the string $r$ has high HILL entropy conditioned on $P$.  That is $H^{\hill}_{\epsilon_{sec}, s_{sec}}(R |P)\geq \tilde{m}$.
\end{itemize}
\end{definition}
Computational fuzzy conductors can be converted to computational fuzzy extractors using standard techniques~(see \apref{sec:further defs}).
The following theorem states the construction is a computational fuzzy conductor~(proof in \apref{sec:construction analysis}).
\begin{theorem}
\label{thm:main thm first cons}
Let $n$ be a security parameter. Let $\mathcal{Z}$ be an alphabet where $|\mathcal{Z}| \ge 2^{ \omega(\log(n))}$.
Let $\mathcal{W}$ be a family of $(q,\alpha= \omega(\log n),  \beta)$-unguessable block sources over $\mathcal{Z}^\gamma$, for any $q = \poly(n)$.  Furthermore, let $C$ be a $(t, \delta_{code})$-Z code over $\mathcal{Z}^\gamma$.  Let $\mathcal{O}$ be an $\gamma$-composable VGB obfuscator for point functions with auxiliary inputs. Then for any $s_{sec} = \poly(n)$ there exists some $\epsilon_{sec}=\ngl(n)$ such that \consref{cons:first construction} is a $(\mathcal{Z}^\gamma, \mathcal{W}, \tilde{m}=H_0(C)-\beta, t)$-computational fuzzy conductor that is $(\epsilon_{sec}, s_{sec})$-hard with error $\delta_{code} + \gamma/|\mathcal{Z}|$.
\end{theorem}

@@

We adapt the definition of Boyen to the computational setting~(\defref{def:outsider fuzz ext}).  
The definition of Boyen considers a single adversary.  We split the adversary into two parts, one of which is information-theoretic and another that is computationally bounded.  The functions $f_2,..., f_q$ can be thought of as a single adversary that sees all prior state.  However, to provide meaningful security in the computational setting, we cannot have communication between $f_2,..., f_q$ and $D$.  This is because $f_2,..., f_q$ are computationally unbounded and thus could break any security that only holds against computationally bounded adversaries.
Because these two adversaries do not communicate we strengthen the definition by allowing the perturbation functions,  $f_i$, to see the original sample $w_1$.\footnote{An alternative would be to have a single computationally bounded adversary that provides perturbation functions but does not see the original reading $w_1$ as in the definition of Boyen.  \consref{cons:sampling} satisfies this alternative adaption as well.}  This was not allowed in the definition of Boyen as it would make security impossible.
